---
title: "U. Albany Confucius Institute Fall 2020 Seminar on US-China Relations in the 21st Century"
description: |
  My discussion with Barry Naughton (UCSD) about industrial policy and low-carbon energy technologies in China
date: 10-09-2020
preview: "title_slide.png"
categories:
  - China
  - Technology
format: html
toc: false
---

```{r}
#| label: setup
#| message: false
#| warning: false
#| include: false

source(here::here("_common.R"))

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.retina = 3,
  comment = "#>"
)
```

[Barry Naughton](https://gps.ucsd.edu/faculty-directory/barry-naughton.html) (Sokwanlok Chair of Chinese International Affairs at the School of Global Policy and Strategy, UCSD) and I kicked off the U. of Albany [Confucius Institute Fall 2020 Seminar Series](https://www.albany.edu/confucius/US-china-relations-fall2020.html) on "_US-China Relations in the 21st Century_" with a discussion about industrial policy and low-carbon energy technologies in China. In his presentation titled, "_China's Industrial Policy: New Technological Revolution or Old-fashioned Protectionism?_", Professor Naughton highlighted some of the recent major technology and industrial policy changes under President Xi and the implications for the U.S. In my talk titled, "_China's key role in scaling low carbon energy technologies_," I discussed the critical role China has played in scaling up the mass production of low-carbon energy technologies, such as solar photovoltaic cells and lithium-ion batteries, highlighting key points from my related [paper in _Science_](https://iopscience.iop.org/article/10.1088/1748-9326/aba715/pdf) with Jonas Nahm.

```{r}
#| echo: false

icon_link(
    icon = "fa fa-file-pdf",
    text = "Slides as PDF",
    url  = "https://filedn.com/lYURdAnVcCykBHec07i0c6j/slides/2020_10_09_helveston_confucius_institute.pdf"
)
icon_link(
    icon = "fa fa-file-pdf",
    text = "Science Paper",
    url  = "https://iopscience.iop.org/article/10.1088/1748-9326/aba715/pdf"
)
```

<iframe width="640" height="600" src="https://u.pcloud.link/publink/show?code=XZqIdeXZCh4KxAo6M10nFln5MelSvSkmh117" frameborder="0" allow="accelerometer; encrypted-media; gyroscope; picture-in-picture" allowfullscreen scrolling="no"></iframe>
