---
title: "Healthier ❤️ & Happier 😄 Hands 🙌"
description: |
  My talk on Software and Hardware Solutions for More Ergonomic Typing for the 2021 useR! Conference
date: "2021-07-06"
preview: "title-slide.png"
categories:
  - productivity
  - keyboards
  - R
format: html
toc: true
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(distilltools)

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.retina = 3,
  comment = "#>"
)
```

I prepared an "Elevator Pitch" (aka lightning talk) for the [2021 useR! Conference](https://user2021.r-project.org/) where I discussed a quick overview of software and hardware solutions for more ergonomic typing. The recording and slides are below. 

See also my related [blog post](https://www.jhelvy.com/posts/2021-07-03-in-search-of-keyboard-nirvana/) for more details on the topics covered in the talk.

# Talk 

<iframe width="560" height="420" src="https://www.youtube.com/embed/WPLEdpSaBAI" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

# Slides

My slides were built using the [{xaringan}](https://github.com/yihui/xaringan) R package. You can see the source code for the slides [here](https://github.com/jhelvy/2021-useR-healthy-hands).

```{r, echo=FALSE}
icon_link(
    icon = "fas fa-external-link-alt",
    text = "Full screen slides",
    url  = "https://jhelvy.github.io/2021-useR-healthy-hands/"
)
icon_link(
    icon = "fa fa-file-pdf",
    text = "Slides as PDF",
    url  = "https://github.com/jhelvy/2021-useR-health-hands/raw/main/2021-useR-healthy-hands.pdf"
)
```

Keyboard Shortcuts for Slides:

- Use <kbd>←</kbd> and <kbd>→</kbd> to navigate through the slides.
- Use <kbd>f</kbd> to toggle full screen.
- Use <kbd>o</kbd> to view an overview of all slides.
- Use <kbd>h</kbd> to see a list of other shortcuts.

```{r slides, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "https://jhelvy.github.io/2021-useR-healthy-hands/index.html",
  ratio = "16:9")
```
